Untitled

### 2022-05-11 Manuscript/Lanuza_et_al_2021.Rmd
keep from here

---
title: \singlespacing \vspace{-1.6cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

@@

Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020]. However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@salguero2016]. Despite the recent advances in the theoretical understanding of the major floral trade-offs [e.g., floral economic spectrum; @roddy2021], we lack empirical evidence that helps to elucidate the spectrum of reproductive trait variation at a global scale as done recently for other vegetative and physiological traits [@diaz2016; @onoda2017].

Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with pollinators at large scales [@sargent2008; @rech2016; @salguero2016; @ruger2018]. Because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different pollinator groups [as done similarly in @dehling2016], we could help to improve our understanding of plant-pollinator associations. Further, there is increasing interest in understanding drivers of plant-pollinator interactions using trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016]. However, plant reproductive traits have been overlooked for most pollination systems [@dellinger2020] and remains unclear how specific plant reproductive biology traits (i.e., mating or compatibility system) influence plant-pollinator associations [@tur2013; @devaux2014].

>>>>

---
title: \singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

@@

Flowering plants have an astonishing diversity of floral structures [@barrett2002; @schiestl2013] that shape plant-pollinator associations [@fenster2004; @dellinger2020]. However, not all reproductive trait combinations are possible due to evolutionary and ecological constraints [@salguero2016]. Despite the recent advances in the theoretical and empirical understanding of the macroecological correlations between plant reproductive traits [@friedman2020; @roddy2021], their study is often limited to a handful number of reproductive traits that are rarely studied jointly. Thus, in order to progress towards a comprehensive understanding of the reproductive spectrum of trait variation as done recently for other vegetative and physiological plant traits [@wright2004; @chave2009; @diaz2016; @onoda2017; @laughlin2021], there is a need to acquire a multitrait perspective with broad geographical coverage that allows elucidating the reproductive spectrum of trait variation of flowering plants.

Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018]. The use of 
trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions. Interestingly, because the species' morphology can determine the species' functional role,

because the species' morphology can determine the species' functional role, by linking the plant's position in the reproductive trait-space with the different floral visitor groups [as done in @dehling2016], we can investigate how the different reproductive trait correlations from the reproductive spectrum associate with the distinct floral visitor groups. However, plant reproductive traits remain overlooked for a great number of plant species [@dellinger2020] and is still unclear how specific reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014].

### 2022-05-11 Supplementary_Material/Sup_Mat_Lanuza_et_al_2021_Ecology_Letters.Rmd
keep from here

---
#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}

@@

## Trade-offs among plant reproductive traits determine interactions with floral visitors

>>>>

---
#title: \singlespacing \vspace{-2.5cm} \LARGE \textbf{Covariation among reproductive traits in flowering plants determine interactions with floral visitors}

@@

## Covariation among reproductive traits in flowering plants determine interactions with floral visitors
